### 2021-05-24 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Final revision - conclusion + appendix
Last fixes

\section{Tezos}\label{sec:tezos}
The Tezos blockchain is presented in its whitepaper as a \enquote{generic and self-amending crypto-ledger} \cite{goodman_tezos_2014}. It uses a proof-of-stake consensus mechanism, which is not only used to agree on the current state of its ledger, but also allows its stakeholders to come to a consensus about changes in the economic protocol by participating in a voting process. The changes included in a protocol upgrade, called amendment, can influence, i.a., which transactions are valid on the blockchain, the payment system or even the voting process itself. It does so without risking a fork of the blockchain. Everyone owning the cryptocurrency of Tezos, called Tez, is considered a stakeholder and can participate in the consensus mechanism. The whitepaper compares the self-amending protocol of Tezos to a game created by Philosopher Peter Suber called ``Nomic'', whose set of rules are subjected to a democratic voting system \cite{nomic}. Similar concepts can also be found in modern pop culture, such as the virtual sports league ``Blaseball'' \cite{blaseball}, which became popular during the COVID-19 pandemic.

In addition to user accounts associated with a public key, Tezos supports smart contracts, which are written in the built-in language Michelson. Tezos' transaction fee system is similar to Ethereum's \cite{wood_ethereum_2021} - it is gas-instrumented and besides a base fee, every operation and byte of storage during contract execution has to be paid for by the user. However, Tezos imposes a hard cap on the amount of gas that can be consumed per operation (including internal transactions) \cite{tezos_docs}\cite{morley_repo}, whereas Ethereum limits the gas quota only in respect to blocks \cite{wood_ethereum_2021}.\\
Tezos is written in the multi-paradigm programming language OCaml. Compiling its source code yields five essential binaries: the  node, baker, endorser, accuser and client. The node is the entity connecting to the peer-to-peer network and keeping a copy of the chain. Bakers are responsible for producing new blocks, the endorsers for validating new blocks and the accusers to call out bakers or endorsers which double-sign or -endorse. The client provides a command line interface to interact with nodes through remote procedure calls (RPC).

@@

Since the Michelson language and interpreter are implemented in the protocol-specific libraries of Tezos, adding new instructions require a protocol update. This entails adding the new instruction to the list of tokens, adding one or several selection rules to the interpreter and typing rules to the type checker \cite{tezos_repo}. Furthermore, the protocol must specify the gas cost of its computation. Previous extensions to the Michelson language, such as the addition of the instruction ``\texttt{DIG n}'' in protocol 005 Babylon \cite{tezos_michelson_ext}, can be used as a guideline for the extension. The gas cost specification of existing instructions \cite{tezos_repo_gas} should be used as an orientation in specifying the costs of new instructions.

@@

To simplify the compilation, the generated code of the assertion body and the parameter type can be plugged into a template containing the necessary boilerplate code for a contract. Such a template is shown in \lstref{lst:contract_templ} --- the placeholders \texttt{<?>} mark the locations where the individual code is inserted. Since assertions do not use any storage as of now, the storage type is set to unit. Lines 3-5 prepare the stack, s.t. the parameter and storage are the two top elements. The lines below the placeholder for the body leave the stack according to calling convention, i.e., the program returns an empty list of internal operations and the unit storage.
\lstinputlisting[label=lst:contract_templ, language=Michelson, caption=Template code for assertion contracts in Michelson, numbers=left]{listings/assertion_template.tz}

>>>>

\section{Introduction to Tezos}\label{sec:tezos}
The Tezos blockchain is presented in its whitepaper as a \enquote{generic and self-amending crypto-ledger} \cite{goodman_tezos_2014}. It uses a proof-of-stake consensus mechanism, which is not only used to agree on the current state of its ledger, but also allows its stakeholders to come to a consensus about changes in the economic protocol by participating in a voting process. The changes included in a protocol upgrade, called amendment, can influence, i.a., which transactions are valid on the blockchain, the payment system or even the voting process itself. It does so without risking a fork of the blockchain. Everyone owning the cryptocurrency of Tezos, called Tez, is considered a stakeholder and can participate in the consensus mechanism. The whitepaper compares the self-amending protocol of Tezos to a game created by Philosopher Peter Suber called ``Nomic'', whose set of rules are subjected to a democratic voting system \cite{nomic}. Similar concepts can also be found in modern pop culture, such as the virtual sports league ``Blaseball'' \cite{blaseball}, which became popular during the COVID-19 pandemic.

In addition to user accounts associated with a public key, Tezos supports smart contracts, which are written in the built-in language Michelson. Tezos' transaction fee system is similar to Ethereum's \cite{wood_ethereum_2021} - it is gas-instrumented and besides a base fee, every operation and byte of storage during contract execution has to be paid for by the user. However, Tezos imposes a hard cap on the amount of gas that can be consumed per operation (including internal transactions) \cite{tezos_docs}\cite{morley_gasmodel}, whereas Ethereum limits the gas quota only in respect to blocks \cite{wood_ethereum_2021}.\\
Tezos is written in the multi-paradigm programming language OCaml. Compiling its source code yields five essential binaries: the  node, baker, endorser, accuser and client. The node is the entity connecting to the peer-to-peer network and keeping a copy of the chain. Bakers are responsible for producing new blocks, the endorsers for validating new blocks and the accusers to call out bakers or endorsers which double-sign or -endorse. The client provides a command line interface to interact with nodes through remote procedure calls (RPC).

@@

Since the Michelson language and interpreter are implemented in the protocol-specific libraries of Tezos, adding new instructions require a protocol update. This entails adding the new instruction to the list of tokens, adding one or several selection rules to the interpreter and typing rules to the type checker \cite{tezos_repo}. Furthermore, the protocol must specify the gas cost of its computation. Previous extensions to the Michelson language, such as the addition of the instruction ``\texttt{DIG n}'' in protocol 005 Babylon \cite{tezos_michelson_ext}, can be used as a guideline for the extension. The gas cost specification of existing instructions should be used as an orientation in specifying the costs of new instructions.

@@

To simplify the compilation, the generated code of the assertion body and the parameter type can be plugged into a template containing the necessary boilerplate code for a contract. Such a template is shown in \lstref{lst:contract_templ} --- the placeholders \texttt{<?>} mark the locations where the individual code is inserted. Since assertions do not use any storage as of now, the storage type is set to unit. Lines 3-5 prepare the stack, s.t. the parameter and storage are the two top elements. The lines below the placeholder for the body leave the stack according to calling convention, i.e., the program returns an empty list of internal operations and the unit storage.
\lstinputlisting[label=lst:contract_templ, language=Michelson, float, caption=Template code for assertion contracts in Michelson, numbers=left]{listings/assertion_template.tz}
